---
title: Slides and course notes
---

{{< include ../_links.qmd >}}

```{r}
#| echo: false
#| include: false
knitr::opts_chunk$set(echo = FALSE)
library(gt)
library(lubridate)
source("../_yaml_extract.R")
dat <- read_yaml("_course.yml")
extract_course(dat)
```


## Schedule 

```{r}
check <- character(0)
schedule <- schedule_df %>%
  rowwise() %>%
  mutate(
    day = case_match(
      session,
      1 ~ "mon",
      2 ~ "wed",
      3 ~ "thu"
    ),
    qmd_file = ifelse(
      identical(
        str_subset(
          list.files("slides", pattern = "qmd", full.names = TRUE),
          pattern = sprintf("lec-%1$.2d-%2$x", week, session)
        ),
        check
      ),
      NA,
      str_subset(
        list.files("slides", pattern = "qmd", full.names = TRUE),
        pattern = sprintf("lec-%1$.2d-%2$x", week, session)
      )
    ),
    lecture_file = ifelse(!is.na(qmd_file),
      gsub("qmd", "slides.html", qmd_file),
      NA
    ),
    notes_file = ifelse(!is.na(qmd_file),
      gsub("qmd", "notes.html", qmd_file),
      NA
    ), ,
    lecture = !is.na(lecture_file)
  ) %>%
  ungroup() %>%
  mutate(
    Material = case_when(
      session != 3 & lecture == TRUE ~ glue("<a class='fa fa-display' href='{lecture_file}' target='_blank'></a> <a class='fa fa-note-sticky' href='{notes_file}' target='_blank'></a>"),
      session == 3 ~ reading,
      TRUE ~ ""
    ),
    Topic = ifelse(is.na(topic), "", topic),
    Assessment = ifelse(is.na(assessment), "", assessment),
    Reading = ifelse(is.na(reading), "", reading),
    Date = as.Date(
      case_when(
        week > 20 ~ NA,
        day == "wed" & week <= 6 ~ ymd(dat$date_start) + weeks(week),
        day == "wed" & week > 6 ~ ymd(dat$date_start) + weeks(week + 1),
        day == "mon" & week <= 6 ~ ymd(dat$date_start) + weeks(week) - days(2),
        day == "mon" & week > 6 ~ ymd(dat$date_start) + weeks(week + 1) - days(2),
        day == "thu" & week <= 6 ~ ymd(dat$date_start) + weeks(week) + days(1),
        day == "thu" & week > 6 ~ ymd(dat$date_start) + weeks(week + 1) + days(1)
      )
    ),
    wk = ifelse((week %% 2) == 0, "a", ifelse(week < 20, "b", "c"))
  ) %>%
  select(Date, Topic, Material, Assessment, week, wk)

midsem_break <- 6 # after which week

schedule |>
  gt() |>
  cols_hide(c(week, wk)) |>
  fmt_markdown(columns = c("Topic", "Material", "Assessment")) |>
  fmt_date(
    columns = Date,
    date_style = "MMMd",
    locale = "en"
  ) |>
  data_color(
    columns = wk,
    method = "factor",
    target_columns = everything(),
    palette = c("lightblue", "grey80", "pink")
  ) |>
  #  tab_row_group(
  #    label = "Reading week",
  #    rows = (midsem_break * 2 + 2):26
  #  ) |>
  # row_group_order(groups = c(NA, "Reading week")) |>
  cols_width(
    Date ~ px(50),
    Material ~ px(20)
  ) |>
  sub_missing(missing_text = "") |>
  tab_options(
    table.width = pct(100),
  )
```

## About slides {{< fa display >}} and notes {{< fa note-sticky >}}

### Slides {{< fa display >}} 

Slides in `revealjs` format (html). If you want then as a pdf (*note you might loose some functionality or contents due to tabs and scroll sections*):

1. Open the slides in your browser from a link on this page
2. Press `e` to get into the PDF export mode (*`?print-pdf` should appear near the end of the url and white borders should appear*)
1. Open the in-browser print dialog (CTRL/CMD+P).
1. Change the `Destination` setting to `Save as PDF`.
1. Change the `Layout` to `Landscape`.
1. Change the `Margins` to `None`.
1. Enable the Background graphics option (if you want it)
1. Click Save 🎉

### Notes {{< fa note-sticky >}}

Content of the slides in html format as a self-contained downloadable file and including tabs and scroll sections. 

More importantly, notes have the commenting and annotateing tools activated via <https://hypothes.is/>. If you create a free account , you can annotate and comment slides as well as share your annotations/comments with the public or via private or public groups.
